1. Write an SQL query, with correlation names, to produce the following output.
```{r}
# Necessary Packages
library(DBI)
library(RSQLite)

# Connect to DB
drv <- dbDriver("SQLite")
Tiny_Clothes <- dbConnect(drv, dbname="Tiny_Clothes.sqlite")
dbListTables(Tiny_Clothes)
Tiny_Clothes <- dbConnect(RSQLite::SQLite(), "Tiny_Clothes.sqlite")

dbGetQuery(Tiny_Clothes, "SELECT product.PROD_NO, NAME, COLOR, ORDER_NO, QUANTITY 
                           FROM product 
                           JOIN sales_order_line 
                           ON product.PROD_NO = sales_order_line.PROD_NO")
```
2. Choose primary keys and foreign keys for the relations:
CUSTOMER, PRODUCT, SALES_ORDER and SALES_ORDER_LINE

CUSTOMER:
Primary key: CUST_NO
Foreign key: none

PRODUCT:
Primary key: PROD_NO
Foreign key: none

SALES_ORDER:
Primary key: ORDER_NO
Foreign key: CUST_NO

SALES_ORDER_LINE:
Primary key: ORDER_NO, PROD_NO
Foreign key: ORDER_NO, PROD_NO

3. Retrieve details of employees who are between 31 years of age and 65 years of age.
```{r}
dbGetQuery(Tiny_Clothes, "SELECT * FROM employee WHERE age BETWEEN 31 and 65")
```
4. How many customers does ‘Tiny Clothes’ have?
```{r}
dbGetQuery(Tiny_Clothes, "SELECT COUNT(*) as num_customers FROM customer")
```
5. Are there any customers in the database whose address is missing?
```{r}
dbGetQuery(Tiny_Clothes, "SELECT COUNT(*) as num_missing FROM customer WHERE ADDRESS IS NULL")

# no addresses are missing
```
6. Which orders are invoiced for a quantity of 10 000 or more items?
```{r}
dbGetQuery(Tiny_Clothes, "SELECT ORDER_NO FROM invoices WHERE QUANTITY >= 10000")

# orders 1 and 2
```
7. Sort EMPLOYEE by age, in descending order.
```{r}
dbGetQuery(Tiny_Clothes, "SELECT * FROM employee ORDER BY AGE DESC")

```
8a.  Using appropriate correlation names, retrieve all names from CUSTOMER
```{r}
dbGetQuery(Tiny_Clothes, "SELECT NAME FROM CUSTOMER")
```
8b. Modify your name to return NAME as FIRST_NAME.
```{r}
dbGetQuery(Tiny_Clothes, "SELECT NAME AS FIRST_NAME FROM CUSTOMER")
```
8c. What happens if you use FIRST NAME?
```{r}
dbGetQuery(Tiny_Clothes, "SELECT NAME AS FIRST NAME FROM CUSTOMER")

# I get a syntax error since there is a space in the column name, which is not allowed unless quotations are used
```

