**Exercise 1: **
Load the necessary packages and open a connection to the Chinook database housed in the sqlite file in the data folder.
```{r}
# Necessary Packages
library(DBI)
library(RSQLite)

# Connect to DB
drv <- dbDriver("SQLite")
chinook_db <- dbConnect(drv, dbname="Chinook_Sqlite.sqlite")
dbListTables(chinook_db)
```
**Exercise 2: Terminology**

a) 
Primary keys uniquely identify records (rows) in a table
Foreign keys establish relationships between tables. takes you from one table to the primary key of another

b)
primary/ foreign key relationships model real world relationships often seen between related objects

c)
SQL - Structure Query Language. This is a programming language that allows us to interact with relational databases.

SQLite - a specific implementation of SQL  (has many different implementations with unique features)

RSQLite - Package within R which allows us to run SQL queries. SQLite Interface for R

**Exercise 3: Tables and Foreign Keys**
(a) List all tables in the database
```{r}
dbListTables(chinook_db)
```
b) List all of the foreign key relationships in the database. How many are there in all?
Write out these relationships in the following format:
TableName.ForeignKey -> TargetTableName.PrimaryKey
```{r}
dbGetQuery(chinook_db, "pragma table_info('Album')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Album')")
dbGetQuery(chinook_db, "pragma table_info('Artist')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Artist')")
dbGetQuery(chinook_db, "pragma table_info('Customer')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Customer')")
dbGetQuery(chinook_db, "pragma table_info('Employee')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Employee')")
dbGetQuery(chinook_db, "pragma table_info('Genre')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Genre')")
dbGetQuery(chinook_db, "pragma table_info('Invoice')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Invoice')")
dbGetQuery(chinook_db, "pragma table_info('InvoiceLine')")
dbGetQuery(chinook_db, "pragma foreign_key_list('InvoiceLine')")
dbGetQuery(chinook_db, "pragma table_info('MediaType')")
dbGetQuery(chinook_db, "pragma foreign_key_list('MediaType')")
dbGetQuery(chinook_db, "pragma table_info('Playlist')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Playlist')")
dbGetQuery(chinook_db, "pragma table_info('PlaylistTrack')")
dbGetQuery(chinook_db, "pragma foreign_key_list('PlaylistTrack')")
dbGetQuery(chinook_db, "pragma table_info('Track')")
dbGetQuery(chinook_db, "pragma foreign_key_list('Track')")
```
```{r}

```

```{r, results = FALSE}
tables <- dbListTables(chinook_db)

tables
for (tbl in tables){
  print(dbGetQuery(chinook_db, paste0("pragma foreign_key_list(",tbl,")")))
}

```
1. Album.ArtistID -> Artist.ArtistID
2. Customer.SupportRepId -> Employee.EmployeeId
3. Employee.ReportsTo -> Employee.EmployeeId
4. Invoice.CustomerId -> Customer.CustomerId
5. InvoiceLine.TrackId -> Track.TrackId
6. InvoiceLine.InvoiceId -> Invoice.InvoiceId
7. PlaylistTrack.TrackId -> Track.TrackId
8. PlaylistTrack.PlaylistId -> Playlist.PlaylistId
9. Track.MediaTypeId -> MediaType.MediaTypeId
10. Track.GenreId -> Genre.GenreId
11. Track.AlbumId -> Album.AlbumId

**Exercise 4: SQL queries**
(a) Select the CustomerId, FirstName, LastName, State, Country of all customers living in California.
```{r}
dbGetQuery(chinook_db, 'SELECT CustomerId, FirstName, LastName, State, Country FROM Customer WHERE State = "CA"')
```
b) How many customers are from USA?
```{r}
dbGetQuery(chinook_db, 'SELECT CustomerId, FirstName, LastName, State, Country FROM Customer WHERE Country = "USA"')
```
13 Customers are from the USA

**Exercise 5: SQL queries**
Choose another table from the database. Write a SQL query and describe in words wat your
query is doing.
```{r}
dbGetQuery(chinook_db, 'SELECT EmployeeId, FirstName, LastName, State, Country FROM Employee')
```
This query is showing the Employee ID and First and Last names of the employees, and the state and country in which each of them are.

**Extra Practice Exercises**
1. Using the course database TinyClothesDB
a) Write down the schema for each of the relations CUSTOMER, PRODUCT, SALES_ORDER_LINE.
```{r}
Tiny_Clothes <- dbConnect(RSQLite::SQLite(), "Tiny_Clothes.sqlite")
CUSTOMER <- read.csv("Tinyclothes Database Files-20230228/CUSTOMER.txt")
print(CUSTOMER)
PRODUCT <- read.csv("Tinyclothes Database Files-20230228/PRODUCT.txt")
print(PRODUCT)
SALES_ORDER_LINE <- read.csv("Tinyclothes Database Files-20230228/SALES_ORDER_LINE.txt")
print(SALES_ORDER_LINE)
```
Schema for CUSTOMER:
CUST_NO
NAME
ADDRESS

Schema for PRODUCT:
PROD_NO
NAME
COLOR

Schema for SALES_ORDER_LINE:
ORDER_NO
PROD_NO
QUANTITY

b) Identify the primary key for each relation and any foreign keys for each relation.

CUSTOMER:
primary key: CUST_NO
foreign key: none

PRODUCT:
primary key: PROD_NO
foreign key: none

SALES_ORDER_LINE:
primary key: ORDER_NO
foreign key: PROD_NO

c) Suggest suitable domain for each attribute of PRODUCT.
PROD_NO: (1,inf)
NAME: {PANTS, SOCKS, SHIRTS}
COLOR: {BLUE, KHAKI, GREEN, WHITE}

2. Find the age of the oldest employee at ‘Tiny Clothes’
```{r}
print(EMPLOYEE)
dbGetQuery(Tiny_Clothes, 'SELECT AGE FROM EMPLOYEE ORDER BY AGE DESC limit 1')
# oldest employee is 65
```
3. Are there any employees under the age of 50 whose name contains the letter ‘R’?
```{r}
dbGetQuery(Tiny_Clothes, 'SELECT NAME FROM EMPLOYEE WHERE AGE < 50')
# No, there are no employees under the age of 50 whose name contains the letter ‘R
```
4. Retrieve the employment number of the sales department manager.
```{r}
print(DEPARTMENT)
dbGetQuery(Tiny_Clothes, 'SELECT MANAGER FROM DEPARTMENT WHERE NAME = "Sales"')
# employment number is E5
```
5. How many departments are there at ‘Tiny Clothes’ ?
```{r}
print(DEPARTMENT)
# 3 departments
```
6. What is Carol’s customer number?
```{r}
print(CUSTOMER)
dbGetQuery(Tiny_Clothes, 'SELECT CUST_NO, NAME FROM CUSTOMER WHERE NAME = "CAROL"')
# Carol's customer number is C3
```
7. Who works in Department D2?
```{r}
print(EMPLOYEE)
dbGetQuery(Tiny_Clothes, 'SELECT EMP_NO, NAME, DEPT_NO FROM EMPLOYEE WHERE DEPT_NO = "D2"')
# Brown works in D2
```
8. Should Tiny Clothes sell PINK SOCKS? How would you answer if you were asked this question by a non-technical manager?
```{r}
print(PRODUCT)
print(SALES_ORDER_LINE)
# no they shouldn't sell pink socks since so far they only sell blue and green clothes, and not very many socks
```
9. Retrieve the employment number of the sales department manager.
```{r}
print(DEPARTMENT)
dbGetQuery(Tiny_Clothes, 'SELECT MANAGER FROM DEPARTMENT WHERE DEPT_NO = "D3"')
# sales department manager's employment number is E5
```

