1. Find the phone extension for all employees named BROWN.
```{r}
# Necessary Packages
library(DBI)
library(RSQLite)

# Connect to DB
drv <- dbDriver("SQLite")
Tiny_Clothes <- dbConnect(drv, dbname="Tiny_Clothes.sqlite")
dbListTables(Tiny_Clothes)
Tiny_Clothes <- dbConnect(RSQLite::SQLite(), "Tiny_Clothes.sqlite")


dbGetQuery(Tiny_Clothes, "select employee.emp_no, name, extension
           from employee
           join employee_phone
           on employee.emp_no = employee_phone.emp_no
           where name = 'BROWN'")
```
2. Find the name and phone extension of the ACCOUNTS manager.
```{r}
dbGetQuery(Tiny_Clothes, "select * from department")
dbGetQuery(Tiny_Clothes, "select * from employee")
dbGetQuery(Tiny_Clothes, "select * from employee_phone")
```
3. Find the names and phone extension of all employees who share an office.

4. Choosing a suitable customer number, add a new customer Charles, whose address is ATLANTIC to the database.

5. What are the attribute names of CUSTOMER?

6. What are the data types of attributes of PRODUCT?